A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
Changing to the new results image
Modifs

\begin{align*}
L(x \rightarrow \Theta) = L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_s(x, \Theta \leftrightarrow \Phi) L(r(x, \Phi) \rightarrow -\Phi) d\omega_\Phi
\end{align*}

@@

The algorithm computes $L$ as follow: first, it chooses one random direction $\Phi$ based on the pdf $p$. Then, it applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops either when a light or a maximal number of bounces has been reached.
%ASK: euh, c'est L ou L_r%
%c'est bon de dire que ça s'arrete au light%

@@

\begin{equation*}
f_r(x, \Theta \leftrightarrow \Phi) L(x \leftarrow \Phi) cos(N_x, \Phi).
\end{equation*}

It is a product of three functions that can be efficiently sampled individually but that are hard to sample when they are combined. The most common strategy used to sample $\Omega_x$ is to use the BRDF (combined with the cosine) because we know it: it is given as an input of the algorithm, for exemple with textures.

@@

@@

>>>>

\begin{align*}
L(x \rightarrow \Theta) &= L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_s(x, \Theta \leftrightarrow \Phi) L(r(x, \Phi) \rightarrow -\Phi) d\omega_\Phi \\
&= L_e(x \rightarrow \Theta) + L_r(x \rightarrow \Theta)
\end{align*}

@@

The algorithm computes $L$ as follow: first, it chooses one random direction $\Phi$ based on the pdf $p$. Then, it applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when a maximal number of bounces has been reached.
%ASK: euh, c'est L ou L_r%
%c'est bon de dire que ça s'arrete au light%

@@

\begin{equation*}
f_s(x, \Theta \leftrightarrow \Phi) L(r(x, \Phi) \rightarrow -\Phi).
\end{equation*}

It is a product of two functions that can be efficiently sampled individually but that are hard to sample when they are combined. The most common strategy used to sample $\Omega_x$ is to use the function $f_s$ because we know it: it is given as an input of the algorithm, for exemple with textures that describe materials.

@@

\begin{center}
\includegraphics[scale=0.5]{images/importance_points.png}
\end{center}

@@

\begin{center}
\includegraphics[scale=0.17]{images/skel_based_rt.png}
\end{center}

This image is a zoom that allows us to see more precisely the the reduction of noise for our method.

\section{Conclusion}
